Contextual Combinatorial Cascading Bandits

### 2015-11-26 contextual combinatorial cascading bandits.tex
write an outline proof under main theorem

Here is our main theorem.
\begin{theorem}
Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq 1$ and regularization parameter $\lambda \geq C_\gamma$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT}),
\end{equation}
where
\begin{align*}
f^* &= \min_{1 \leq t \leq T} f_t^*\\
C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
\end{align*}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d\log(C_\gamma T)\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

\begin{lemma}
\label{lem:increasing} 
If $0= \gamma_0 \leq \gamma_1 \leq ... \leq \gamma_{K-1} \leq 1$ and we have $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A\in\cS$,
$$
f(A, w) \leq f(A, w').
$$
\end{lemma}
\begin{proof}
It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&~~-\gamma_{k-1} + \sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + \prod_{j=k+1}^{m}w_j'\\
&\geq \gamma_{k-1} (-1 + \sum_{i=k+1}^m (\prod_{j=k+1}^{i-1}w_j')(1- w_i') +  \prod_{j=k+1}^{m}w_j')\\
&=\gamma_{k-1} \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&~~\gamma_{k-1} (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k\prod_{j=k+1}^{m}w_j'\\
& \leq \gamma_{k-1} (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k'\prod_{j=k+1}^{m}w_j'.
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
&=\sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j)(1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k) \\
&\qquad + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k\prod_{j=k+1}^{m}w_j']\\
&\leq \sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j) (1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k') \\
&\qquad + w_k'\sum_{i=k+1}^m \gamma_{i-1} (\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k'\prod_{j=k+1}^{m}w_j']\\
&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
\end{align*}
Then we obtain the result.
\end{proof}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
$$
f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
$$
where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m=1$.
\begin{align*}
&~~f(m+1, w)\\
&= f(m, w) -\prod_{k=1}^{m} w_k + \gamma_{m}  (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f(m, p) +  \sum_{k=1}^{m} \gamma_k' u_k + (\gamma_{m} - 1) (1 - p_{m+1}) \prod_{k=1}^{m} p_k\\
&~~ + (1 - \gamma_{m}) u_{m+1}\\
&\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
\end{align*}
\end{proof}

Let $p_A$ denote the probability that all of items in $A$ are observed. Then $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$.

@@

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

>>>>

Here is our main theorem.
\begin{theorem}
Given partial reward parameters $0 = \gamma_0 \leq \gamma_1 \leq \cdots \gamma_{K-1} \leq c f^*$ and regularization parameter $\lambda \geq C_\gamma$ for some constant $\frac{1}{2} < c < 1$, for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, {\it ConComCascade}, satisfies
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT}),
\end{equation}
where
\begin{align*}
f^* &= \min_{1 \leq t \leq T} f_t^*\\
C_\gamma &= \sum_{k=1}^{K} \gamma_k'^2 = \sum_{k=1}^{K-1} (1 - \gamma_k)^2 = O(K).
\end{align*}
\end{theorem}

To prove this theorem, we want to estimate $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. If the chosen action $\bA_t$ is not suboptimal, which is equivalent to $\Delta_{t, \bA_t} > 0$, then we must have
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
$$
From the above relation, we need the following two lemmas to derive an estimate of $\Delta_{t, \bA_t}$ in terms of all elements in $\bA_t$.

\begin{lemma}
\label{lem:increasing} 
Given parameters $0= \gamma_0 \leq \gamma_1 \leq ... \leq \gamma_{K-1} \leq 1$, $f(A, w)$ is increasing with respect to $w$; equivalently, suppose $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, we have for any $A\in\cS$,
$$
f(A, w) \leq f(A, w').
$$
\end{lemma}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
$$
f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
$$
where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
\end{lemma}

From lemma \ref{lem:increasing} and $\theta_*^{\top}x_t \leq \bU_t$ by lemma \ref{lem:estimateU}, we can deduce 
\begin{equation}
\label{eq:fIncrease}
f(A_t^*, \theta_*^{\top}x_t) \leq f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t).
\end{equation}
Further from lemma \ref{lem:estimateTech}, we can deduce
\begin{equation}
\label{eq:fTech}
f(\bA_t, \bU_t) \leq f(\bA_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k
\end{equation}
where $u_k = \beta_{t-1}(\delta)\norm{x_{t, \ba_k^t}}_{\bV_{t-1}^{-1}}$. Combining equation (\ref{eq:fIncrease})) and (\ref{eq:fTech})), we can conclude that
$$
\Delta_{t, \bA_t} = f(A_t^*, \theta_*^{\top}x_t) - f(\bA_t, \theta_*^{\top}x_t) \leq \sum_{k=1}^{\abs{\bA_t}} \gamma_k' u_k.
$$

However, this estimate involves all elements of $\bA_t$. Only when the learning agent has observed all elements of $\bA_t$, we can use such an estimate, which means we are able to estimate
$$
\EE[\Delta_{t, \bA_t}] = \EE[\Delta_{t, \bA_t}(1/p_{\bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}].
$$
Problem might happen if $p_{\bA_t}$ is small. Thus we need the following lemma to find a good substitution of $\bA_t$.

\begin{lemma}
\label{lem:prefixExist}
Suppose the weights for items in $E$ are $w = (w_a)_{a \in E}$. Let $A = (a_1, ..., a_{\abs{A}})$ be a list and let $p_A$ denote the probability that all of items in $A$ are observed; equivalently, $p_A = \prod_{k=1}^{\abs{A}-1}w(a_i)$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for any given constant $\frac{1}{2} < c < 1$, there exists a prefix $B$ of $A$ such that
$$
p_B \geq c f^* - \gamma_{\abs{B}}, \qquad \Delta_B \geq \frac{1}{2} \Delta_A,
$$
where
$$
f^* = \max_{A'} f(A', w), \qquad \Delta_{A'} = f^* - f(A', w).
$$
\end{lemma}

From this lemma, we can find a prefix $\bB_t$ of $\bA_t$ such that $p_{B_t}$ is large enough and $\Delta_{\bB_t}$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$, we can get an estimate of $R(T)$. We leave all details in the next subsection.

\subsection{Proofs}

\begin{proof}[ of lemma \ref{lem:increasing}]
It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&~~-\gamma_{k-1} + \sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + \prod_{j=k+1}^{m}w_j'\\
&\geq \gamma_{k-1} (-1 + \sum_{i=k+1}^m (\prod_{j=k+1}^{i-1}w_j')(1- w_i') +  \prod_{j=k+1}^{m}w_j')\\
&=\gamma_{k-1} \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&~~\gamma_{k-1} (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k\prod_{j=k+1}^{m}w_j'\\
& \leq \gamma_{k-1} (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k'\prod_{j=k+1}^{m}w_j'.
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
&=\sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j)(1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k) \\
&\qquad + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k\prod_{j=k+1}^{m}w_j']\\
&\leq \sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j) (1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k') \\
&\qquad + w_k'\sum_{i=k+1}^m \gamma_{i-1} (\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k'\prod_{j=k+1}^{m}w_j']\\
&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
\end{align*}
Then we obtain the result.
\end{proof}

\begin{proof}[ of lemma \ref{lem:estimateTech}]
We prove this by induction. It holds obviously for $m=1$.
\begin{align*}
&~~f(m+1, w)\\
&= f(m, w) -\prod_{k=1}^{m} w_k + \gamma_{m}  (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f(m, p) +  \sum_{k=1}^{m} \gamma_k' u_k + (\gamma_{m} - 1) (1 - p_{m+1}) \prod_{k=1}^{m} p_k\\
&~~ + (1 - \gamma_{m}) u_{m+1}\\
&\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
\end{align*}
\end{proof}

\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
&\leq 4 \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d\log(C_\gamma T)\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

@@

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
%\nocite{langley00}
